---
title: "P8105 Homework 5"
author: "Grace Liu"
date: "11/8/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(purrr)
library(skimr)
library(knitr)
```

## Problem 1 
```{r participant data, include=FALSE}
dataframe = 
  list.files("./data", pattern = "*.csv", full.names = TRUE) %>% 
  map(read_csv)

for (i in 1:20) {
  if (i <11) {
   dataframe[[i]] = dataframe[[i]] %>% 
     mutate(arm = "Control", study_id = i)
   }
  if (i >10) {
    dataframe[[i]] = dataframe[[i]] %>% 
      mutate(arm = "Experimental", study_id = i-10)
    }
}

participant_data =
  dataframe %>% 
  reduce(rbind) %>% 
  gather(key = week, value = observation, week_1:week_8) %>% 
  separate(week, into = c("remove", "week"), sep = "_") %>% 
  mutate(week = as.numeric(week), study_id = as.character(study_id)) %>% 
  janitor::clean_names() %>% 
  select(arm, study_id, week, observation)
```

```{r study line graph, fig.align='center', echo=FALSE}
participant_data %>% 
  group_by(arm, study_id) %>% 
  ggplot(aes(x = week, y = observation, type = study_id, color = arm)) + 
    geom_line() +
  theme_minimal() +
    theme(legend.position = "bottom") +
    labs(x = "Week", y = "Observations", 
         title = "Observations for each subject, by week and study arm")
```

The figure above details the observations of 20 study participants over eight weeks. Half the participants were assigned to the control arm, and the other half were assigned to the experimental arm. Early in the study, there was not much difference between the two study arms. However, as the weeks passed, the observations for all individuals in the experimental arm increased, even as no appreciable change was seen in participants in the control arm.  

## Problem 2
```{r homicide data, include=FALSE}
homicides = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  mutate(city_state = paste(city, state, sep = ", ")) %>% 
  transform(reported_date = as.Date(as.character(reported_date), "%Y%m%d"), 
            victim_age = as.numeric(victim_age)) %>% 
  select(uid, reported_date, city_state, everything()) %>% 
  janitor::clean_names()

homicides_summary =
  homicides %>% 
  group_by(city_state) %>% 
  summarise(total_homicides = n(),
            unsolved_a = sum(disposition == "Closed without arrest"),
            unsolved_b = sum(disposition == "Open/No arrest")
            ) %>% 
  mutate(unsolved = unsolved_a + unsolved_b) %>% 
  select(-unsolved_a, -unsolved_b)

#One observation has an invalid location (Tulsa, AL). Since it can't be determined if this should be "Tulsa, OK" or "Birmingham, AL", I am dropping the observation from the datasets.

homicides = subset(homicides, city_state != "Tulsa, AL")
homicides_summary = subset(homicides_summary, city_state != "Tulsa, AL")
```

This dataset contains details on `r format(nrow(homicides), big.mark=",")` homicides occurring in `r nrow(homicides_summary)` major US cities between `r min(homicides$reported_date)` and `r max(homicides$reported_date)`. 

The city with the highest number of total homicides was `r homicides_summary$city_state[match(max(homicides_summary$total_homicides), homicides_summary$total_homicides)]`, where there were a total of `r format(max(homicides_summary$total_homicides), big.mark=",")` homicides over the decade. The city with the lowest number of total homicides was `r homicides_summary$city_state[match(min(homicides_summary$total_homicides), homicides_summary$total_homicides)]`, with `r min(homicides_summary$total_homicides)` cases. On an absolute scale, `r homicides_summary$city_state[match(max(homicides_summary$unsolved), homicides_summary$unsolved)]` was also the city with the most unsolved homicides and `r homicides_summary$city_state[match(min(homicides_summary$unsolved), homicides_summary$unsolved)]` had the least number of unsolved homicides. In terms of cities with the highest and lowest proportion of total homicides that remain unsolved, `r round(max(homicides_summary$unsolved/homicides_summary$total_homicides)*100, digits=2)`% of
`r homicides_summary$city_state[match(max(homicides_summary$unsolved/homicides_summary$total_homicides), homicides_summary$unsolved/homicides_summary$total_homicides)]`'s cases are still unsolved, compared to `r round(min(homicides_summary$unsolved/homicides_summary$total_homicides)*100, digits=2)`% of
`r homicides_summary$city_state[match(min(homicides_summary$unsolved/homicides_summary$total_homicides), homicides_summary$unsolved/homicides_summary$total_homicides)]`'s cases.

In addition to location and report date, this dataset includes information on the race, age, and sex of each victim. Of the `r format(nrow(homicides), big.mark=",")` victims, `r format(nrow(subset(homicides, victim_sex == "Female")), big.mark=",")` (`r round(nrow(subset(homicides, victim_sex == "Female"))/nrow(homicides)*100, digits = 2)`%) were female and `r format(nrow(subset(homicides, victim_sex == "Male")), big.mark=",")` (`r round(nrow(subset(homicides, victim_sex == "Male"))/nrow(homicides)*100, digits = 2)`%) were male. The average age of all victims was `r round(mean(homicides$victim_age, na.rm = TRUE), digits=2)`, with the oldest and youngest victims being `r max(homicides$victim_age, na.rm = TRUE)` and `r min(homicides$victim_age, na.rm = TRUE)` years old, respectively. A further breakdown of victims by race, age, and sex, is included below:

```{r victim descriptions, echo=FALSE}
homicides %>% 
  group_by(victim_race) %>%
  summarise(
    total = n(),
    average_age = mean(victim_age, na.rm = TRUE),
    male = sum(victim_sex == "Male", na.rm = TRUE),
    female = sum(victim_sex == "Female", na.rm = TRUE),
    sex_unknown = sum(victim_sex == "Unknown", na.rm = TRUE)
  ) %>% 
  knitr::kable(digits = 2, format.args = list(big.mark=","))
```

```{r prop.test function, include=FALSE}
prop_unsolved = 
  function(homicides_summary) {
    prop.test(homicides_summary$unsolved, homicides_summary$total_homicides, conf.level = 0.95) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)
  }
```

The table below shows the estimated proportion, and confidence intervals, of homicides within Baltimore, MD, that remain unsolved. An estimated `r round((homicides_summary %>% filter(city_state == "Baltimore, MD") %>% prop_unsolved() %>% select(estimate))*100, digits = 2)`% of homicides are unsolved.
```{r baltimore prop_unsolved, echo=FALSE}
homicides_summary %>% 
  filter(city_state == "Baltimore, MD") %>% 
  prop_unsolved() %>% 
  knitr::kable(digits = 4)
```


<!-- For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe. -->

<!-- Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city. -->

<!-- Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides. -->

